Describing the scale and composition of calls for service in Detroit

### 2021-09-01 paper.Rmd
map legend and writing

---
title: "Describing the scale and composition of calls for service in Detroit"
author: "Samuel Langton (Netherlands Institute for the Study of Crime and Law Enforcement)"
bibliography: refs.bib
output:
  # word_document: default
  pdf_document: default
header-includes: \usepackage{lscape}
csl: apa.csl
abstract: In the spirit of a recent contribution by Ratcliffe (2021) published in
  _Crime Science_ this short paper describes the scale and composition of public demand
  for police services in Detroit, United States, during 2019. Findings broadly confirm
  those by Ratcliffe, namely, that a considerable proportion of police time is spent
  resolving a diverse array of calls for service, including public
  health incidents. The temporal and spatial patterning of different types of public
  demand for police services are often distinct. The data and code to replicate analyses
  are made openly available.
---

@@

Individual incident location coordinates were aggregated to synthetic grid cells laid over the city to generate heatmaps of counts throughout the year. ^[Grid cells were defined as 1000 ft$^2$ (305m$^2$) -- a size deemed appropriate based on a balance between capturing localised variation and interpretable visualisations. 2% of incidents were excluded from the spatial visualisations due to incomplete geographic information.] These are visualised for each demand classification in Figure 3.

- Community: Wayne State University buildings.
- Crime: Henry Ford Hospital, including the emergency department.
         The hotspot in the far east is also a hosptial, as is the north west one.
- Proactive: Wayne State University buildings, Midtown neighbourhood, just outside
  downtown.
- Quality of life: university disticts, downtown detroit and financial district.
- Health: downtown, universities, schools and detroit rescue mission ministries

>>>>

---
title: "Describing the scale and composition of calls for service in Detroit"
author: "Samuel Langton (Netherlands Institute for the Study of Crime and Law Enforcement)"
bibliography: refs.bib
output:
  word_document: default
  # pdf_document: default
header-includes: \usepackage{lscape}
csl: apa.csl
abstract: In the spirit of a recent contribution by Ratcliffe (2021) published in
  _Crime Science_ this short paper describes the scale and composition of public demand
  for police services in Detroit, United States, during 2019. Findings broadly confirm
  those by Ratcliffe, namely, that a considerable proportion of police time is spent
  resolving a diverse array of calls for service, including public
  health incidents. The temporal and spatial patterning of different types of public
  demand for police services are often distinct. The data and code to replicate analyses
  are made openly available.
---

@@

Individual incident location coordinates were aggregated to synthetic grid cells laid over the city to generate heatmaps of counts throughout the year. ^[Grid cells were defined as 1000 ft$^2$ (305m$^2$) -- a size deemed appropriate based on a balance between capturing localised variation and interpretable visualisations. 2% of incidents were excluded from the spatial visualisations due to incomplete geographic information.] These are visualised for each demand classification in Figure 3. While there is overlap, call hotspots and the degree of concentration differs between types of public demand. Calls about community issues concentrate overwhelmingly in and around the Wayne State University (WSU). Crime calls tend to cluster near hospitals, most notably, the Henry Ford Hospital in the city centre. Proactive call activity originates from the WSU area and Midtown, and quality of life around WSU and downtown. Health calls concentrate in downtown, but also around WSU and in the vicinity of the Detroit Rescue Mission Ministries, a large facility for the vulnerable, abused and homeless people in the city.
